Submission HW1

### 2022-08-31 hw1-1/submission.Rmd

###

>>>>

### Vanilla knn model

We implement vanilla knn model here, with rectangular kernel and majority voting (i.e probability threshold \>0.5) among neighbors to decide predicted label.

```{r}
# Rectangular(unweighted) kernel as optimised 
knn_pred <- vector(mode="list",length = dim(knn_data)[1])
pred_table <- data.frame(k_val=numeric(0),acc_val=double(0)) #dataframe to hold accuracy with k
for (k0 in seq(1,nrow(knn_data),by=25)){ #To loop over k values
  for (i in 1:nrow(knn_data)){ #To loop over indvidual data points
    knn_model_v0<-kknn(R1~.,train = knn_data[-i,],test = knn_data[i,],k=k0,kernel="rectangular",scale = TRUE)
    knn_pred[i]<-as.integer(round(fitted(knn_model_v0),digits = 0)==knn_data$R1[i]) #majority voting > 0.5
  }
  percent_accuracy<-round(as.double(sum(unlist(knn_pred)))/nrow(knn_data),digits =2)
  pred_table[nrow(pred_table)+1,]=c(k0,percent_accuracy)
}
plot(pred_table)
```

The graph above here plots Accuracy on y-axis vs 'k'. As we increase the k, Accuracy is mostly static and after a certain threshold, it starts dropping almost linearly to 55%, where it then stabilizes. The 55% number here is intuitive since with as many nearest neighbors as the #data points, the prediction decision basically boils down to assigning the majority label in the dataset, i.e. Negative. Therefore, for 55% the negative class, we receive a correct prediction while the rest 45% Positive class is misclassified.

### Optimisation over 'k' and probability threshold
